---
title: "our_data_in_ranges"
author: "JR"
date: "11/3/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(GenomicRanges)
source("/scratch/Shares/rinnclass/CLASS_2022/JR/CLASS_2022/util/plotting_functions.R")
source("/scratch/Shares/rinnclass/CLASS_2022/JR/CLASS_2022/util/_setup.R")
source("/scratch/Shares/rinnclass/CLASS_2022/JR/CLASS_2022/util/intersect_functions.R")
library(Gviz)
library(ggpubr)
library(ggplot2)
```


Alright time to start digging into the data for new results !!
We have made a consensus peak file for each DBP and 
Moreover, we have a data frame of a bunch of peak overlap features for each DBP.

# Loading in filtered consensus peaks

First let's load in the consensus peak files (this is something we always have to do)

```{r loading consensus peaks}
# read in file list to lapply import below
# first create a file list of filtered consensus peaks
fl <- list.files("/scratch/Shares/rinnclass/CLASS_2022/data/filtered_consensus_peaks",
                                             pattern = "*.bed",
                                             full.names = TRUE) #done
# # lappy to import each file in file list 
filtered_consensus_peaks <- lapply(fl, rtracklayer::import) #done
# fl <- list.files("/scratch/Shares/rinnclass/CLASS_2022/JR/CLASS_2022/class_exeRcises/analysis/11_consensus_peaks/filtered_consensus_peaks/", full.names=TRUE)
# 
# # loading each consensus peak bed file into a list of GRanges
# filtered_consensus_peaks <- lapply(fl, rtracklayer::import, format = "bed")
# Let's take a look since this is an important first step.
# Ok we should probably add some names -- another common task.
# we can get name from @elementdata$listdata$name
filtered_consensus_peaks[[40]]$name %>%
  head()
# cool now we can strsplit this to get the name 
# on the left of  x_ [1] indicates take the left
# let's use strplit to clean the name up by splitting on _
?strsplit
# let's add names to our consensus peaks list of GRanges
# selecting the left of the split with index [1]
names(filtered_consensus_peaks) <- sapply(filtered_consensus_peaks, function(x){
  unlist(strsplit(x$name, "_"))[[1]]
})
# Now we have a named list of consensus peaks in the environment -- let's take a look
```

# loading in num_peaks_df
Let's load in our num_peaks_df and decide if we want to filter?
```{r num_peaks_df}
# loading in our previous analyses:
num_peaks_df <- read.csv("/scratch/Shares/rinnclass/CLASS_2022/<your_folder>/CLASS_2022/class_exeRcises/analysis/12_peak_features/num_peaks_df.csv")
# num_peaks_df <- read.csv("/scratch/Shares/rinnclass/CLASS_2022/JR/CLASS_2022/class_exeRcises/analysis/12_peak_features/num_peaks_df.csv")
```


# Let's plot some data and see what we might learn
Ok enough set up let's dig in with making some plots!


```{r plotting peak features}
# First let's look at a histogram of peak#/DBP
 ggplot(num_peaks_df, aes(x = num_peaks)) + 
  geom_histogram(bins = 70)
```



# plotting num_peaks versus genome coverage.
? What would you suspect would happen
```{r peaks vs coverage}
# Let's plot our result of num_peaks versus genome coverage.
ggplot(num_peaks_df, aes(x = num_peaks, y = total_peak_length, label = dbp)) +
  geom_point() + 
  geom_smooth(method = "gam", se = TRUE, color = "black", lty = 2)+
              #formula = 'y ~ x') +
  # geom_text() +
  ylab("BP covered") +
  xlab("Number of peaks") +
  ggtitle("Peak count vs. total bases covered")
# saving MAKE SURE WORKING DIRECTORY IS CORRECT
ggsave("figures/peak_num_vs_coverage_notextgam.pdf")
# Feel free to copy code from 14_plotting_R_part_I.Rmd for other versions of this figure.
```

# plotting num peaks on promoters
Let's did in a bit deeper and see how coverage on promoters.
```{r number of DBPS on promoters}
# now let's plot x as num_peaks and y num overlapping promoters.
ggplot(num_peaks_df,
       aes(x = num_peaks, y = peaks_overlapping_promoters)) +
  
  xlab("Peaks per DBP") +
  ylab("Number of peaks overlapping promoters") +
  ggtitle("Relationship Between Number of DBP Peaks and Promoter Overlaps")+
  geom_point() +
  geom_abline(slope = 1, linetype="dashed") +
  geom_smooth(method = "lm", se=F, formula = 'y ~ x',
              color = "#a8404c") +
  stat_regline_equation(label.x = 35000, label.y = 27000) +
  ylim(0,60100) +
  xlim(0,60100)
ggsave("figures/3_peak_num_vs_promoter_coverage.pdf")
# we observe a "saturation of binding events -- as you get more
# peaks you stop increaseing binding to promoters.
# maybe it leaks into the gene body let's check
```


# peak Coverage on gene bodies
```{r peak coverage on gene bodies}
ggplot(num_peaks_df,
       aes(x = num_peaks, y = peaks_overlapping_genebody)) +
# code to make things pretty
  xlab("Peaks per DBP") +
  ylab("Number of peaks overlapping genes") +
  ggtitle("Number of DBP Peaks vs Gene Body Overlaps")+
  geom_point() +
  geom_abline(slope = 1, linetype="dashed") +
  geom_smooth(method = "lm", se=F, formula = 'y ~ x',
              color = "#a8404c") +
  stat_regline_equation(label.x = 35000, label.y = 15000) +
  ylim(0,60100) +
  xlim(0,60100)
# Interesting result !! Gene bodies explain almost all the places of binding in 
# the genome! Where as promoters had a non linear asymptope after a certain number 
# of peaks. VERY COOL and surprising. There are billions of other possible binding sites!
ggsave("figures/4_peak_num_vs_gene_body_coverage.pdf")
```

Ok so we have started generating results in this handy num_peaks_df. 
However, the peak_occurence_df is also very handy for analyses.
Let's load it in and do some analyses -- THIS ONE IS REALLY COOL :).

# Reading in Peak occurence df

```{r read in peak_occurence_df}
# First read the file into an object
peak_occurence_df <- read.csv("/scratch/Shares/rinnclass/CLASS_2022/EricY/bchm/exercises/analysis/12_peak_features/peak_occurence_dataframe.csv")
# peak_occurence_df <- read.csv("/scratch/Shares/rinnclass/CLASS_2022/JR/CLASS_2022/class_exeRcises/analysis/12_peak_features/peak_occurence_dataframe.csv")
# let's have a look. This is a summary of the peak occurence df.
# we did colsums to find how many binding events there are at each promoter
# so the last column will tell us how many binding events there were at a given promoter. 
```


Let's make a density plot of num DBPs bound per promoter
# Density plot of binding events
```{r density plot of DBP localization events}
# Since we are making a density plot we only need the X axis.
ggplot(peak_occurence_df, aes(x = number_of_dbp)) +
  geom_density(alpha = 0.2, color = "#424242", fill = "#424242") +
  # theme_paperwhite() +
  theme_minimal() + 
  xlab(expression("Number of DBPs")) +
  ylab(expression("Density")) +
  ggtitle("Promoter binding events",
          subtitle = "mRNA and lncRNA genes") 
# Wow what a result! Last year we only saw up to 111 binding events at a promoter
# this is kind of validated where the first peak in the distribution falls at 100
# binding events -- yet there is a second distribution of regions of 300 or more 
# binding events -- wonder what those are :) ?
# VERY COOL let's print out the figure
ggsave("figures/num_binding_events_per_promoter.pdf")
```


Lets find how many promoters don't have any DBPs bound
# promoters with out binding events

```{r prmoters with out binding events}
# here is just a simple index and filter of the index to have at least 1 dbp bound.
unbound_promoters <- peak_occurence_df %>% 
  filter(peak_occurence_df$number_of_dbp < 1)
# how many are there?
nrow(unbound_promoters); nrow(peak_occurence_df)
# so there are only a few 6,747 promoters that don't have binding evetns (~10%)
#  let's put it in a folder called results. We will always use this folder structure
write_csv(unbound_promoters, "results/unbound_promoters.csv")
```


# Do any DBPs never bind a promoter?
```{r is there a DBP that doesn't bind promoters?}
# we actually don't need code for this we can look in num_peaks_df and sort :)
# There are only a few and we may want to filter these out above.
```

# lncRNA versus mRNA promoter binding
Let's compare the binding patterns of lncRNA vs mRNA promoters.
While we are at it let's do some deep dives into the aes layer
This is required to make two plots in one :)

```{r}
# Plotting lncRNA -vs mRNA promoter binding distribution
# for more advanced figure making check out the code below.
# it is not the best practice to do to many analyses in ggplot.
# The below esxample shows how powerful and flexible ggplot is.
ggplot(num_peaks_df, aes(x = num_peaks)) +
  geom_point(aes(y = peaks_overlapping_lncrna_promoters), color = "red") +
  geom_point(aes(y = peaks_overlapping_mrna_promoters), color = "black") +
  stat_regline_equation(aes(y = peaks_overlapping_lncrna_promoters), color = "red") +
  stat_regline_equation(aes(y = peaks_overlapping_mrna_promoters), color = "black", label.y = 20000) +
  geom_smooth(aes(y = peaks_overlapping_lncrna_promoters), method = "lm", se = FALSE, formula = "y ~ x") +
  geom_smooth(aes(y = peaks_overlapping_mrna_promoters), method = "lm", se = FALSE, formula = "y ~ x") +
  theme_minimal()
ggsave("figures/lncRNA-mRNA-promoter_binding.pdf")
# Nice we see that mRNA promoters have about 4x more binding (from slope)
# Both follow a fairly linear trend except mRNA may have saturate quicker.
# This is just a fancier version of the same thing -- not mutate to clean up names
# this first part is manipulating the num peaks df with pivot longer
num_peaks_dfl <- num_peaks_df %>%
  dplyr::select(-peaks_overlapping_promoters) %>%
  # selecting these to cols to pivot longer
  pivot_longer(cols = peaks_overlapping_lncrna_promoters:peaks_overlapping_mrna_promoters,
               names_to = "gene_type",
               values_to = "peaks_overlapping_promoters") %>%
  mutate(gene_type = gsub("peaks_overlapping_", "", gene_type))
# plotting
ggplot(num_peaks_dfl, aes(x = num_peaks, y = peaks_overlapping_promoters, 
                         col = gene_type)) +
         geom_point() +
         geom_abline(slope = 1, linetype="dashed") +
  geom_smooth(method = "lm", se = FALSE, formula = "y ~ x") +
  stat_regline_equation() +
  scale_color_manual(values = c("#a8404c", "#424242"))+
  xlab("Peaks per DBP") +
  ylab("Peaks Overlapping Promoters") +
  ggtitle("Number of DBP Peaks and Promoter Overlaps") +
  theme_minimal() + theme(legend.position ="bottom")
#ggsave("figures/peaks_overlaps_relationship_by_gene_type.png", height = 5, width = 8)
ggsave("figures/peaks_overlaps_relationship_by_gene_type.pdf", height = 5, width = 8)
``` 

############
exeRcise:
############

Make a figure of percentage of peaks for each DBP that overlap promoters & gene bodies.
Add these columns to num_peaks_df---
title: "14_plotting_R_I"
author: "JR"
date: "11/2/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggpubr)
library(tidyverse)
source("/scratch/Shares/rinnclass/CLASS_2022/JR/CLASS_2022/util/plotting_functions.R")
source("/scratch/Shares/rinnclass/CLASS_2022/JR/CLASS_2022/util/_setup.R")

```

One of the best parts of R is the plotting abilities. You are, by analogy designing your own figures with code. You can run many stastical analyses and plot the outputs in the code to make a figure. Here we will focus on GGPLOT(GGPLOT2). The GG says it all:

"Grammar of Graphics" -- it truly is a very pure and flexible way of plotting data for figures!

There are 8 possible layers of information -- each building on the data layer that you are importing. This looks really confusing but we will slowly build up from the basics (mapping, stats, geom)

Plotting layers of R:

1) Data -- data being plotted from object indexes etc.

2) MAPPING -- mapping data (aes)

3) Statistics -- statical analyses on mapped data

4) scales -- how big small you want things

5) GEOMETRIES -- what type of plots you are making (geom)

6) Facets -- making multiple representations of plots

7) Coordinates -- specifing placement of image aspects

8) THEME -- a set version of colors, background. Mostly so you don't have to add many of the layers above everytime!

Ok let's walk through some simple examples to more difficult figures using these layers!

Layer 1 : DATA (data types matter so good to label object accrodingly)

# loading in num_peaks_df

```{r loading in num_peaks_df}
# before we get started let's import that data we are going to plot. 
# Let's load in the num_peaks_df from our previous class (13_ChIP_peak_features)

num_peaks_df <- read_csv('/scratch/Shares/rinnclass/CLASS_2022/JR/CLASS_2022/class_exeRcises/analysis/12_peak_features/num_peaks_df.csv')

```

# GGPLOT basics
Now let's start plotting in GGplot!

```{r ggplot basics}
# let's make this simple plot first: number of peaks -vs- total peak length

ggplot(num_peaks_df, aes(x = num_peaks,
                         y = total_peak_length)) +
  geom_point()


?ggplot
# ggplot first wants the data parameter, then an 'aesthetics' layer (aes)
# aes() layer needs everything you want to do with the data. The + adds the next layer.
```

# changing shapes in plot
Now let's change the shape of the points outside the aes() layer and in the geom() layer
```{R changing shapes in plot}
             
ggplot(num_peaks_df, aes(x = num_peaks, 
                 y = total_peak_length)) +
         
           geom_point(shape = 'square',
             color = 'purple')


# Here are some good resources for other shapes and color vignettes:
# http://www.sthda.com/english/wiki/ggplot2-point-shapes



```

# coloring by data in aes() layer
We colored the plot above in the geom layer, but what if we wanted to color by "is_tf"?
Since that depends on the data we need to do that in the aes() layer!
We can even index and run functions in aes()
```{R # coloring by data in aes() layer}
# Let's plot the num_peaks -vs- coverage for Zinc finger proteins (C2H2 ZF)

ggplot(num_peaks_df, aes(x = num_peaks, 
                 y = total_peak_length,
                 color = dbd == "C2H2 ZF")) +
  geom_point()

```

```{R adding function in aes() layer}
#simple function in the aes()
ggplot(num_peaks_df, aes(x = log2(num_peaks/1e3), 
                 y = total_peak_length/1e6,
                 color = dbd == "C2H2 ZF")) +
  geom_point()

# Wow that sure looks differnt :) of note the inflection point
# indicates at a certain point the trend is not as linear as we saw before.

```

# facet in ggplot by TF annotation
We can also plot each type of data in a column by using the 'facet' function.
Let's plot three plots for if DBP is a TF, is not or NA.

```{R facet by TF annotation}

ggplot(num_peaks_df, aes(x = num_peaks, 
                 y = total_peak_length
                )) +
  facet_wrap(tf ~ .) +
  geom_point() 
  

# nice we see three plots, one for each category.


```

# Geom layer : histogram
Now let's take a look at other types of plots in the geom layer.
geom_histogram() is very useful in a lot of analyses. Let's start there.

```{r Geome_histogram}

# frequencty of peak numbers across DBPs

ggplot(num_peaks_df, aes(x = num_peaks)) +
  geom_histogram()

# let's add more bins

ggplot(num_peaks_df, aes(x = num_peaks)) +
  geom_histogram(bins = 50)

# Let's chage the color of the bars in histogram by number of peaks.
# again we need to do this inside aes() since the data needs to read.

ggplot(num_peaks_df, aes(x = num_peaks, fill = tf)) +
  geom_histogram(bins = 30)

# this is hard to see the two distributions.
# let's fix this by adding a 'position' parameter in the geom layer.

ggplot(num_peaks_df, aes(x = num_peaks, fill = tf)) +
   geom_histogram(bins = 30, position = "dodge")

# so now we can see the individual data points separated!

```

# # Geom layer : density plot
DENISTY Plots are also very useful to see where the density of data arises.
```{R geom_density()}

ggplot(num_peaks_df, aes(x = num_peaks, fill = tf)) +
   geom_density()

# but again its hard to see let's fix that with shading or alpha in
# geom layer

ggplot(num_peaks_df, aes(x = num_peaks, fill = tf)) +
   geom_density(alpha = 0.1)

# let's change color of the line now (inside aes())

ggplot(num_peaks_df, aes(x = num_peaks, fill = tf, color = tf)) +
   geom_density(alpha = 0.3)

# so now line and fill are same color -- let's see:

ggplot(num_peaks_df, aes(x = num_peaks, fill = tf, color = tf)) +
   geom_density(alpha = 0.0)

```

# Multiple Geom layers 
The geom layer has a lot of options AND you can layer them!
Let's take out x,y plots above and map them into a 2D density plot
```{R geom_point() & geom_density_2d}

ggplot(num_peaks_df, aes(x = num_peaks, 
                 y = total_peak_length)) +
  geom_point()+
  geom_density_2d() 

# This is helpful as it shows us most of the data is in bottom left

# what would happen if we change the order?

ggplot(num_peaks_df, aes(x = num_peaks, 
                 y = total_peak_length)) +
   geom_density_2d()+
    geom_point()

# it's hard to see but in this case the contour is on top
# of points and points are below -- subtle but important

```

# trend lines
Let's add even more geom_*() layers -- starting with a 'trend line'
```{r geom_smooth, geome_abline}

?geom_abline
# This will make a line with a given slope and intercept

?geom_smooth
# This shows variance and deviations of the trend lines

# let's add them both !

ggplot(num_peaks_df, aes(x = num_peaks, 
                 y = total_peak_length)) +
  geom_point() +
  geom_abline(slope = 1000, intercept = 0) +
  geom_smooth(method = "gam")


# cool this fits -- what does it mean?
```

# Bar plots
Let's take a quick look at bar plots 
we provide the x-axis and ggplot counts for Y.
We will also use this opportunity to look at level 3) STAT layer
```{r geom_bar()}

# let's plot the number of each type of DBD in our set of DBPs 

ggplot(num_peaks_df, aes(x = dbd)) + 
  geom_bar()


# If the we want to provide the Y-axis for a specific DBP
# we need to apply stat = identitiy in the geom_bar()

ggplot(num_peaks_df, aes(
      x = dbp,
      y = num_peaks)) +
        geom_bar(stat = "identity")

# basically this allows you to command the y-axis 
# but is very messy in this case


# let's look at a more realistic example when there is categorical data

ggplot(num_peaks_df, aes(x = tf, 
                 y = total_peak_length
                )) +
  geom_point() +
  stat_summary(fun = "mean",
               color = "red",
               shape = 2,
               size = 2)


# We can use a linear model to find the best trend-line

ggplot(num_peaks_df, aes(x = num_peaks, y = total_peak_length)) +
  geom_point() +
  geom_smooth(method = "lm")

# We can get the slope and intercept from making a lm variable:

lm_fit <- lm(num_peaks_df$total_peak_length ~ num_peaks_df$num_peaks)
summary(lm_fit)
# slope = 1,000 
# ORDER MATTERS: if reversed the slope is 8 e -3!




# let's convert the lm_fit data to a data_frame using tidy()
# it's in the library broom:
library(broom)

lm_df <- tidy(lm_fit)
# so much easier to read than summary :)

# plotting with the actual lm fit:
ggplot(num_peaks_df, aes(x = num_peaks, y = total_peak_length)) +
  geom_point() +
  geom_abline(slope = lm_df$estimate[[2]], intercept = lm_df$estimate[[1]])

```

# Summary of where we are at
Now we have gone through these layers:

1) Data -- data being plotted from object indexes etc.

2) MAPPING -- mapping data (aes)

3) Statistics -- statical analyses on mapped data

5) Geom

Now let's look at the scales layer

4) scales -- how big small you want things
Scales is important for outputting specific factors as colors that are "scaled"
alos other outputs need to be scaled such as scale values to the "mean" etc.


# scale layer
?scale

```{r scale layer}

# Let's see how we can use the scales layer to change axes.

ggplot(num_peaks_df, aes(x = log10(num_peaks), y =log10(total_peak_length), color = tf)) +
  geom_point()+
  scale_x_continuous(breaks = c(1, 2, 3, 4)) +
  scale_color_brewer(palette = 3) 

# scale_x_continious (same for y) is calling the scale layer specifically
# We are giving it where to put values on X-axis      


```

# changes axes limits
What if we want to set the limits of the axes? 
We can use 'xlim' & 'ylim' in scale layer.

```{R xlim and ylim}

ggplot(num_peaks_df, aes(x = num_peaks, y = total_peak_length, color = tf)) +
  geom_point() +
  xlim(1e3, 1e5) +
  ylim(5e5, 6e7) +
  scale_color_brewer(palette =  2) 

# coool so we zoomed in!

```

# FACETS
This will allow us to make multiple plots in the same plot frame or facet
One limitation is that it can only make the same plots from different data

Be careful in the facet layer that you don't make too many plots. 
Essentially we make as many figures as there are entries.

FACET_GRID & FACET_WRAP
```{r facet_grid(), facet_wrap()}

# First let's take a look at the top three represented DBDs?
table(num_peaks_df$dbd)[order(table(num_peaks_df$dbd))]

# Now let's set dbds to these three DBDs.
dbds <- c("C2H2 ZF", "Homeodomain", "bZIP")

# Now the plotting beings and good example of running functions in aes()
ggplot(num_peaks_df %>% filter(dbd %in% dbds),
       aes(x = num_peaks, y = total_peak_length )) +
  facet_grid(dbd ~ .) + 
  geom_point()

# here we call facet grid. The parameters are rows and columns separated by ~
# so we said take the DBDs and plot them as rows.
```

We can also facet grid another parameter -- let's say tf

```{R two facets}

ggplot(num_peaks_df %>% filter(dbd %in% dbds),
       aes(x = num_peaks, y = total_peak_length )) +
  facet_grid(dbd ~ tf) + 
  geom_point()



# Here we said plot DBD as rows and tf status as columns -- 
# We can easily flip this too:


ggplot(num_peaks_df %>% filter(dbd %in% dbds),
       aes(x = num_peaks, y = total_peak_length )) +
  facet_grid(tf ~ dbd) + 
  geom_point()

# Thus the ~ is telling which rows and columns are plotted

```

# facet wrap
We just used facet_grid, but we can also use facet_wrap
```{R facet_wrap()}

ggplot(num_peaks_df %>% filter(dbd %in% dbds), 
       aes(x = num_peaks, y = total_peak_length )) +
  facet_wrap(dbd ~ tf) + 
  geom_point()

# difference all combos of each factor. Same as before but facet wrap
# doesn't mind if all the values are in one category. 
# Overall the same plots as facet_grid()
```

# DEEPER INTO FACET: we can add some parameters to order the plots
```{R deeper into facets}

ggplot(num_peaks_df, aes(x = num_peaks, y = total_peak_length )) +
  facet_wrap(tf ~ ., nrow = 3, ncol = 1) + 
  geom_point()

# or 

ggplot(num_peaks_df, aes(x = num_peaks, y = total_peak_length )) +
  facet_wrap(tf ~ ., nrow = 2) + 
  geom_point()

# Note the axis don't scale here -- let's use 'scales = free' parameter

ggplot(num_peaks_df, aes(x = num_peaks, y = total_peak_length )) +
  facet_wrap(tf ~ ., scales = "free", ncol = 1) + 
  geom_point()

```

# Coordinate layer
How to represent X and Y coordinates in different coordinate systems.
This is unlikely to really be used in biological data but an important layer!


R has a bunch of built in "coordinate" systems. We have been using Cartesian 
and it is the most common "coordinate" system.
But you can also plot data in "polar" and other coordinate systems.
We can just add it in the "Coordinates layer"

```{r coordinate layer}

# let's make the coordinates polar instead of cartesian
ggplot(num_peaks_df, aes(x = dbd)) +
  geom_bar() +
  coord_polar()

# the values eminate from the center and are a "bar_plot" from the center.
# we can easily see as we did above C2H2 ZF most represented in our data.

# We can play around in the coordinate space too. 
# For example to tell what is  the "theta" or circular dimension. 

ggplot(num_peaks_df) +
  geom_bar(aes(x = dbd)) +
  coord_polar(theta = 'y')

```

# Theme layer
This is a great way to package all the features you want, colors,
backgrounds, grid lines etc. We tend to use paper white as a defualt theme.

We made a defualt theme that we can source at the begining of the
document call _setup.R. Once loaded a "paper white" theme will be available.

Here is an example of a 'theme' is called in ggPlot

```{r themes}

ggplot(num_peaks_df, aes(x = num_peaks)) + 
  geom_density(alpha = 0.2, color = "#424242", fill = "#424242") +
  theme_paperwhite() +
  xlab(expression("Number of peaks")) +
  ylab(expression("Density")) +
  ggtitle("Promoter binding events",
          subtitle = "mRNA and lncRNA genes")

# Note this example build everything from labels to data presentation!

# Let's take a look at _setup.R
# Nice, it basically calls a "function" in ggplot
# You can change this as you please by going through each line (hint: google)
```

# more themes
There are a number of built-in themes in addition to 
the one we've provided. You can see them by typing theme_ 
then autocomplete and check a few out! Here is cleavland :

```{r more themes}

ggplot(num_peaks_df, aes(x = num_peaks)) +
  geom_density() +
  theme_cleveland()

# we can load our custom theme paper_white
ggplot(num_peaks_df, aes(x = num_peaks)) +
  geom_density() +
  theme_paperwhite()


```

